Simultaneous Elicitation of Scoring Rule and Agent Preferences for Robust Winner Determination

### 2020-12-04 minimax.tex
IJCAI format (some warnings)

%%% LaTeX Template for AAMAS-2021 (based on sample-sigconf.tex)
%%% Prepared by Natasha Alechina and Ulle Endriss (version 2020-08-06)

%%% Start your document with the \documentclass command.
%%% Use the first variant below for the final paper.
%%% Use the second variant below for submission.

\PassOptionsToPackage{hypertexnames=false, pdfusetitle, linkbordercolor={1 1 1}, citebordercolor={1 1 1}, urlbordercolor={1 1 1}}{hyperref}
%\documentclass[sigconf]{aamas} 
\documentclass[sigconf, anonymous]{aamas}

%%% Load required packages here (note that many are included already).
\input{preamble/packages}
%TODO consider removing anyfontsize and mathrsfs when submitting. They are needed for the \mathscr command at Olivier’s box (probably due to some outdated package) and for removing a warning about rsfs font size.
\usepackage{anyfontsize}
\usepackage{mathrsfs,stmaryrd}
%\input{preamble/redac}
%\input{preamble/math_basics}
\input{preamble/math}
%for appendix
\usepackage{import}
\usepackage{algorithm, algpseudocode}

@@

%TODO remove this before submission, check vboxes
\vbadness=10000

%%% AAMAS-2021 copyright block (do not change!)

\setcopyright{ifaamas} 
\acmConference[AAMAS '21]{Proc.\@ of the 20th International Conference on Autonomous Agents and Multiagent Systems (AAMAS 2021)}{May 3--7, 2021}{London, UK}{U.~Endriss, A.~Now\'{e}, F.~Dignum, A.~Lomuscio (eds.)}
\copyrightyear{2021}
\acmYear{2021}
\acmDOI{}
\acmPrice{}
\acmISBN{}

%%% Use this command to specify your EasyChair submission number.
%%% In anonymous mode, it will be printed on the first page.

\acmSubmissionID{554}

@@

\author{Beatrice Napolitano}
\affiliation{
	\institution{Université Paris-Dauphine, Université PSL, CNRS, LAMSADE}
	\city{75016 Paris}
	\state{France}}
\email{beatrice.napolitano@dauphine.fr}

\author{Olivier Cailloux}
\affiliation{
	\institution{Université Paris-Dauphine, Université PSL, CNRS, LAMSADE}
	\city{75016 Paris}
	\state{France}}
\email{olivier.cailloux@dauphine.fr}

\author{Paolo Viappiani}
\affiliation{
	\institution{LIP6, UMR 7606, CNRS and Sorbonne Universit\'e}
	\city{Paris}
	\state{France}}
\email{paolo.viappiani@lip6.fr}

%%% Use this environment to specify a short abstract for your paper.

@@

%%% The code below was generated by the tool at http://dl.acm.org/ccs.cfm.
%%% Please replace this example with code appropriate for your own paper.
%NB Olivier: suppresses the warning.
\settopmatter{printccs=false}
\ccsdesc[500]{Computing methodologies~Knowledge representation and reasoning}

\keywords{Uncertainty in AI, Computational Social Choice, Preference Elicitation}

%%% Include any author-defined commands here.

%%% The following commands remove the headers in your paper. For final 
%%% papers, these will be inserted during the pagination process.

\pagestyle{fancy}
\fancyhead{}
\setlength{\footskip}{1.6cm}
\cfoot{\thepage}

%%% The next command prints the information defined in the preamble.

@@

\paragraph{Comparison of strategies}
\begin{figure}
	\caption{Average MMR in problems of size $(5, 10)$ after $k$ questions.}
	\label{fig:smallSize}
	\Description{Graph showing that Pessimistic performs slightly better than Extended pessimistic, itself performing better than Elitist, itself performing much better than Random.}
	\includegraphics[width=.45\textwidth]{comparison.png}
\end{figure}
\sisetup{table-number-alignment = center, table-figures-integer=2, table-figures-decimal=1, table-auto-round}
\begin{table}
	\caption{Average MMR in problems of size $(10, 20)$ after $k$ questions.}
	\label{tab:biggerSize}
	\begin{tabular}{S[table-figures-integer=3, table-figures-decimal=0]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left, table-figures-integer=1]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left, table-figures-integer=1]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left, table-figures-integer=1]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]}
		\toprule
		{k} & {Rnd.} & {sd} & {Pes.} & {sd} & {Eli.} & {sd} \\
		\midrule
		0 &20.0 & 0.0 & 20.0 & 0.0&  20.0 & 0.0 \\
		50 & 19.82 & 0.04 &	15.59 &0.56	&17.38& 0.7\\
		100 & 19.12	& 0.26&	11.91&	1.26 &15.23& 0.73\\
		150 & 18.06	& 0.47&	8.92&	1.53 &13.38& 1.11\\
		200 & 16.89	& 0.62&6.24&2.02&11.76& 1.03\\
		250 & 15.63 & 0.84&	4.64&1.72&10.56& 0.89\\
		300 & 14.72	& 0.94&	3.01& 1.35 &10.48& 0.87\\
		350 & 13.41	& 1.15& 1.76& 0.95&10.48& 0.86\\
		400 & 11.98	& 0.68&	0.62&0.56 &10.48& 0.86\\
		\bottomrule
	\end{tabular}
\end{table}
\begin{table}
	\caption{Average MMR in problems of size $(10, 20)$ and geometric weights after $k$ questions.}
	\label{tab:geometricWeights}
	\begin{tabular}{S[table-figures-integer=3, table-figures-decimal=0]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left, table-figures-integer=1]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left, table-figures-integer=1]}
		\toprule
		{k} & {Pes.} & {sd} & {Eli.} & {sd} \\
		\midrule
		0	&20.0	&0.0	&20.0	&0.0\\
		50	&15.96	&0.54	&17.26	&0.42\\
		100	&12.48	&0.93	&15.6	&0.43\\
		150	&9.58	&1.37	&13.94	&0.76\\
		200	&7.43	&1.25	&10.95	&1.12\\
		250	&5.26	&1.52	&6.6	&0.79\\
		300	&3.47	&1.32	&6.57	&0.79\\
		\bottomrule
	\end{tabular}
\end{table}
Our first experiment concerns small size situations.
\Cref{fig:smallSize} compares some of our strategies in the case $m = 5, n = 10$ (variations around this size yield similar conclusions), where the results are averaged over $200$ runs.
%(The figure also displays the performance of the Elitist strategy, to which we will come back.)
We see that asking random questions does not allow to reach a low regret level even after having asked 100 questions, whereas a low regret level ($\MMR$ = 1) is reached by Pessimistic before having asked 60 questions.
We also see that Pessimistic performs slightly better than Extended pessimistic, showing that Pessimistic chooses candidate questions wisely; this is good news since Pessimistic is much faster: it takes on average only $16$s for a complete elicitation session (for $m = 5$, $n = 10$ and $100$ questions), while Extended pessimistic takes $50$s. Notice that although they exhibit a close performance, Pessimistic performs consistently better, in the sense that the numbers are systematically in favor of Extended pessimistic when performing the experiment again.
\Cref{tab:biggerSize} shows that these conclusions also hold for a problem of larger size ($m = 10, n = 20$), except that this table does not feature Extended pessimistic, which is too slow to be run repeatedly on such instance.

@@

%\subsection{Decrease in MMR values}
\paragraph{Decrease in MMR values}
\begin{figure}
	\caption{Average MMR after $k$ questions with Pessimistic strategy for different problem sizes.}
	\label{fig:linearity}
	\Description{Graph showing that the MMR decreases very approximately linearly, and is convex, as a function of the number of questions.}
	\includegraphics[width=.45\textwidth]{linearity.png}
\end{figure}

@@

\bibliographystyle{ACM-Reference-Format} 
%TODO remove this when submitting, and consider solving the vertical overflows
\vfuzz=5pt
\bibliography{biblio}
\end{document}

>>>>

\documentclass{article}
\pdfpagewidth=8.5in
\pdfpageheight=11in
% The file ijcai21.sty is NOT the same than previous years'
\usepackage{ijcai21}
\usepackage{times}
\usepackage{soul}

\usepackage[hidelinks]{hyperref}

%%% Load required packages here (note that many are included already).
\input{preamble/packages}
%TODO consider removing anyfontsize and mathrsfs when submitting. They are needed for the \mathscr command at Olivier’s box (probably due to some outdated package) and for removing a warning about rsfs font size.
\usepackage{anyfontsize}
\usepackage{mathrsfs,stmaryrd}
%\input{preamble/redac}
%\input{preamble/math_basics}
\input{preamble/math}
%for appendix
\usepackage{import}
\usepackage{algorithm, algpseudocode}
\usepackage{booktabs}

@@

\pdfinfo{
	/TemplateVersion (IJCAI.2021.0)
}

@@

\author{
	Beatrice Napolitano$^1$\footnote{Contact Author}\and
	Olivier Cailloux$^1$\and
	Paolo Viappiani$^2$\\
	\affiliations
	$^1$Université Paris-Dauphine, Université PSL, CNRS, LAMSADE\\
	$^2$LIP6, UMR 7606, CNRS and Sorbonne Universit\'e\\
	\emails
	\{beatrice.napolitano, olivier.cailloux\}@dauphine.fr,
	paolo.viappiani@lip6.fr
}

@@

@@

\paragraph{Comparison of strategies}
\begin{figure}
	\caption{Average MMR in problems of size $(5, 10)$ after $k$ questions.}
	\label{fig:smallSize}
%	\Description{Graph showing that Pessimistic performs slightly better than Extended pessimistic, itself performing better than Elitist, itself performing much better than Random.}
	\includegraphics[width=.45\textwidth]{comparison.png}
\end{figure}
\sisetup{table-number-alignment = center, table-figures-integer=2, table-figures-decimal=1, table-auto-round}
\begin{table}
	\caption{Average MMR in problems of size $(10, 20)$ after $k$ questions.}
	\label{tab:biggerSize}
	\begin{tabular}{S[table-figures-integer=3, table-figures-decimal=0]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left, table-figures-integer=1]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left, table-figures-integer=1]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left, table-figures-integer=1]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]}
		\toprule
		{k} & {Rnd.} & {sd} & {Pes.} & {sd} & {Eli.} & {sd} \\
		\midrule
		0 &20.0 & 0.0 & 20.0 & 0.0&  20.0 & 0.0 \\
		50 & 19.82 & 0.04 &	15.59 &0.56	&17.38& 0.7\\
		100 & 19.12	& 0.26&	11.91&	1.26 &15.23& 0.73\\
		150 & 18.06	& 0.47&	8.92&	1.53 &13.38& 1.11\\
		200 & 16.89	& 0.62&6.24&2.02&11.76& 1.03\\
		250 & 15.63 & 0.84&	4.64&1.72&10.56& 0.89\\
		300 & 14.72	& 0.94&	3.01& 1.35 &10.48& 0.87\\
		350 & 13.41	& 1.15& 1.76& 0.95&10.48& 0.86\\
		400 & 11.98	& 0.68&	0.62&0.56 &10.48& 0.86\\
		\bottomrule
	\end{tabular}
\end{table}
\begin{table}
	\caption{Average MMR in problems of size $(10, 20)$ and geometric weights after $k$ questions.}
	\label{tab:geometricWeights}
	\begin{tabular}{S[table-figures-integer=3, table-figures-decimal=0]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left, table-figures-integer=1]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left, table-figures-integer=1]}
		\toprule
		{k} & {Pes.} & {sd} & {Eli.} & {sd} \\
		\midrule
		0	&20.0	&0.0	&20.0	&0.0\\
		50	&15.96	&0.54	&17.26	&0.42\\
		100	&12.48	&0.93	&15.6	&0.43\\
		150	&9.58	&1.37	&13.94	&0.76\\
		200	&7.43	&1.25	&10.95	&1.12\\
		250	&5.26	&1.52	&6.6	&0.79\\
		300	&3.47	&1.32	&6.57	&0.79\\
		\bottomrule
	\end{tabular}
\end{table}
Our first experiment concerns small size situations.
\Cref{fig:smallSize} compares some of our strategies in the case $m = 5, n = 10$ (variations around this size yield similar conclusions), where the results are averaged over $200$ runs.
%(The figure also displays the performance of the Elitist strategy, to which we will come back.)
We see that asking random questions does not allow to reach a low regret level even after having asked 100 questions, whereas a low regret level ($\MMR$ = 1) is reached by Pessimistic before having asked 60 questions.
We also see that Pessimistic performs slightly better than Extended pessimistic, showing that Pessimistic chooses candidate questions wisely; this is good news since Pessimistic is much faster: it takes on average only $16$s for a complete elicitation session (for $m = 5$, $n = 10$ and $100$ questions), while Extended pessimistic takes $50$s. Notice that although they exhibit a close performance, Pessimistic performs consistently better, in the sense that the numbers are systematically in favor of Extended pessimistic when performing the experiment again.
\Cref{tab:biggerSize} shows that these conclusions also hold for a problem of larger size ($m = 10, n = 20$), except that this table does not feature Extended pessimistic, which is too slow to be run repeatedly on such instance.

@@

%\subsection{Decrease in MMR values}
\paragraph{Decrease in MMR values}
\begin{figure}
	\caption{Average MMR after $k$ questions with Pessimistic strategy for different problem sizes.}
	\label{fig:linearity}
	%\Description{Graph showing that the MMR decreases very approximately linearly, and is convex, as a function of the number of questions.}
	\includegraphics[width=.45\textwidth]{linearity.png}
\end{figure}

@@

\bibliographystyle{named}
\bibliography{biblio}
\end{document}
